\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-15 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Minor rewriting

     \begin{figure}[H]
     	\centering
     	\vspace{-0.9cm}
     	\small
     	\resizebox{\linewidth}{!}{
     		\input{Figs/3D_hierarchy}
     	}
     	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$. The gray colour two dimensional plane reflects the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that spans $\mathfrak{s}$. The points in $\mathfrak{s}$ represents realisations or coherent forecasts}\label{fig:3D_hierarchy}
     \end{figure}

@@

	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a vector of point forecasts of all series in the hierarchy at time $t+h$, made using information up to and including time $t$. Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
	\end{definition}

@@

	The problem of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.  We will call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|h}$, where the subscript $t+h|h$ implies that the forecast is made as time $t$ for a period $h$ steps into the future.  In the sequel, this subscript will be dropped at times for ease of exposition.  In the most general terms, reconciliation can be defined as follows

@@

	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.  In general a projection matrix has the idemoptence property, i.e. $\bm{SG}^2=\bm{SG}$.  However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped onto itself by that projection. This is a fundamental property of projections and also proved in lemma 2.4 in \citet{rao1974}. In our context this means that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.

	We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.  This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011}.  We refrain from any discussion of regression models focusing instead on geometric interpretations.  However the connection between OLS and orthogonal projection should be clear, in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the data onto the span of the regressors.

@@

	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecast should be `close'.  The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value that is targeted by the forecast.

@@

	The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \cite{WicEtAl2019}.  The discussion in that paper focuses on the case of MinT. Here we provide a new explicit proof of that result first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation by any projection matrix in Section~\ref{sec:oblique}.

@@

	\begin{figure}[H]\label{fig:Schematic_OLSRecon}
		\centering
		\vspace{-0.9cm}
		\tiny
		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$}

@@

	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix.  However this matrix can be considered to be an orthogonal projection for a different geometry, namely the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.  One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.  This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.  The transformed reconciled forecast results from an orthogonal projection in the transformed space since

@@

	Another way of understanding the generalised Euclidean geometry is that it is defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$.  This interpretation is quite instructive when it comes to thinking about the connection between distances and loss functions.  In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.  For diagonal $\bm{W}$, this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix, this is equivalent to a Mahalanobis distance.  As such Theorem~\ref{th:distred} can easily be generalised as follows:

	\begin{theo}[General distance reducing property]\label{th:gdistred}
        If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the generalised Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|_{\bm{W}}$ be the $L_2$ norm (in the generalised Euclidean sense with respect to $\bm{W}$) of vector $\bm{v}$ then:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{\bm W}\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{\bm W}.
		\end{equation}
	\end{theo}
	\begin{proof}
    The proof is identical to the proof for Theorem~\ref{th:distred} but relies on the generalised Pythagorean Theorem (applicable to Generalised Euclidean space) rather than the Pythagorean Theorem.
    \end{proof}

@@

@@

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection showed as in Figure \ref{fig:Orthogonal_projection_all_points}.  Figure \ref{fig:Oblique_projection_all_points} depicts a similar oblique projection along $\bm{R}$ for all the gray points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal is expectation.

@@

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.  \todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.  Our own solution to dealing with biased forecasts is to bias correct, or translate the forecast prior to reconciling via projections.  It is to this approach that we now turn our attention.

%	Representation of a coherent subspace in a three dimensional hierarchy where $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$. The coherent subspace is depicted as a gray two dimensional plane labelled $\mathfrak{s}$. Note that the columns of $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ form a basis for $\mathfrak{s}$. The red points lying on $\mathfrak{s}$ can be either realisations or coherent forecasts.

	\section{Bias correction} \label{sec:BiasCorrection}
	\todo{Need to discuss and rewrite this section since we are using different bias correction method in the empirical study}
	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such we see no problems with using the same errors to bias correct.  Geometrically, the intuition is simple.  In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.

>>>>

     \begin{figure}[H]
     	\centering
     	\vspace{-0.9cm}
     	\small
     	\resizebox{\linewidth}{!}{
     		\input{Figs/3D_hierarchy}
     	}
     	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$. The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that spans $\mathfrak{s}$. The red points in $\mathfrak{s}$ represent realisations or coherent forecasts}\label{fig:3D_hierarchy}
     \end{figure}

@@

	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a vector of point forecasts of all series in the hierarchy where the subscript $t+h|h$ implies that the forecast is made as time $t$ for a period $h$ steps into the future. Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
	\end{definition}

@@

	The problem of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.  We will call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|h}$.  In the sequel, this subscript will be dropped at times for ease of exposition.  In the most general terms, reconciliation can be defined as follows

@@

	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.  In general a projection matrix is defined via the idemoptence property, i.e. $\bm{SG}^2=\bm{SG}$.  However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}. In our context this implies that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.

	We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.  This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011}.  We refrain from any discussion of regression models focusing instead on geometric interpretations.  However the connection between OLS and orthogonal projection should be clear, in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the response onto the span of the regressors.

@@

	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecast should be `close'.  The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.

@@

	The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \cite{WicEtAl2019}.  The discussion in that paper focuses on the case of MinT. Here we provide a new explicit proof of that result.  We do so first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation using any projection matrix in Section~\ref{sec:oblique}.

@@

	\begin{figure}[H]\label{fig:Schematic_OLSRecon}
		\centering
		\vspace{-0.9cm}
		\tiny
		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
		\caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$}

@@

	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix in the usual Euclidean geometry.  However this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm $||\bm{v}||_{{\bm W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, which we will call the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.  One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.  This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.  The transformed reconciled forecast results from an orthogonal projection in the transformed space since

@@

	Thinking of the problem in terms of a geometry defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$ is also quite instructive when it comes to thinking about the connection between distances and loss functions.  In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.  For diagonal $\bm{W}^{-1}$, this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix, this is equivalent to a Mahalanobis distance.  As such Theorem~\ref{th:distred} can easily be generalised as follows:

	\begin{theo}[General distance reducing property]\label{th:gdistred}
        If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the generalised Euclidean sense) projection onto $\mathfrak{s}$ then:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{{\bm W}^{-1}}\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{{\bm W}^{-1}}.
		\end{equation}
	\end{theo}
	\begin{proof}
    The proof is identical to the proof for Theorem~\ref{th:distred} but relies on the generalised Pythagorean Theorem (applicable to Generalised Euclidean space) rather than the Pythagorean Theorem.
    \end{proof}

@@

	{\bf Discuss results in Figure 11 here}

@@

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection showed as in Figure \ref{fig:Orthogonal_projection_all_points}.  Figure \ref{fig:Oblique_projection_all_points} depicts a similar oblique projection along $\bm{R}$ for all the gray points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

@@

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.  \todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.  Opening the door to reconciliation methods that change already coherent base forecast would seem to suggest an increase in the variability of the forecast.  This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance is to reduce variance.

	Our own solution to dealing with biased forecasts is to bias correct {\em before} reconciliation.  In many cases the method for bias correction will be context specific.  For instance, in  our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where bias is induced via taking a Box-Cox transformation before modelling.  In this well-known case a number of bias correction methods exist.  Our particular choice of bias correction will be the Guererro method \citep{guerrero1993time}.

	Alternatively, a more general purpose approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such we see no problems with using the same errors to bias correct.  Geometrically, the intuition is simple.  In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.
